\mytitle

### 2015-07-30 MSc_diss.tex
Minor changes

\begin{figure} % Sillman1999withdotsline and netO3rate_withINORG_NOx_1ppb_100ppb
\centering
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{{./pics/Sillman1999_Fig1_adapted_withdotssquare}.png}
  \captionof{figure}{Isopleths giving net rate of $O_3$ production (ppb/h, solid lines) as a function of $VOC$ (ppbC) and $NO_x$ (ppb) for mean summer daytime meteorology and clear skies. The solid lines represent production rates of 1, 2.5, 5, 10, 15, 20 and 30 ppb/h. Adapted from \citep{Sillman1999}.}\label{fig:Sillman1999}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/noAN/chem_noAN_netO3rate_withINORG_NOx_1ppb_100ppb.png}
  \captionof{figure}{Isopleths giving net rate of $O_3$ production (ppb/h, color) as a function of $VOC$ (ppbC) and $NO_x$ (ppb) in the first modelling experiment with alkyl nitrate chemistry switched off combined with an additional run with inorganic chemistry only (i.e. the only $VOC$ is $CO$).}\label{fig:noAN_netO3_rate}
\end{minipage}
\end{figure}

@@

The same kind of plot can be found in Figure \ref{fig:noAN_netO3_rate}, which is produced using data from our model from the first experiment with alkyl nitrate chemistry switched off. Taking into account the fact that the maximum $NO_x$ mixing ratio considered in the experiment is 10 ppb, our results are directly comparable only with a part of the data from Figure \ref{fig:Sillman1999}, namely with those inside the green dashed square. Moreover, since the minimum $NO_x$ mixing ratio considered in the experiment is 5 ppt, while the corresponding value in Figure \ref{fig:Sillman1999} is 1 ppb, a negative $O_3$ production rate is seen in our results, whereas it stays out of range of Figure \ref{fig:Sillman1999}.

@@

\section{Results} \label{sec:res}

>>>>

\begin{figure} % Sillman1999withdotsline and netO3rate_withINORG_NOx_1ppb_100ppb
\centering
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{{./pics/Sillman1999_Fig1_adapted_withdotsrectangle}.png}
  \captionof{figure}{Isopleths giving net rate of $O_3$ production (ppb/h, solid lines) as a function of $VOC$ (ppbC) and $NO_x$ (ppb) for mean summer daytime meteorology and clear skies. The solid lines represent production rates of 1, 2.5, 5, 10, 15, 20 and 30 ppb/h. Adapted from \citep{Sillman1999}.}\label{fig:Sillman1999}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/noAN/chem_noAN_netO3rate_withINORG_NOx_1ppb_100ppb.png}
  \captionof{figure}{Isopleths giving net rate of $O_3$ production (ppb/h, color) as a function of $VOC$ (ppbC) and $NO_x$ (ppb) in the first modelling experiment with alkyl nitrate chemistry switched off combined with an additional run with inorganic chemistry only (i.e. the only $VOC$ is $CO$).}\label{fig:noAN_netO3rate}
\end{minipage}
\end{figure}

@@

The same kind of plot can be found in Figure \ref{fig:noAN_netO3rate}, which is produced using data from our model from the first experiment with alkyl nitrate chemistry switched off. Taking into account the fact that the maximum $NO_x$ mixing ratio considered in the experiment is 10 ppb, our results are directly comparable only with a part of the data from Figure \ref{fig:Sillman1999}, namely with those inside the green dashed square. Moreover, since the minimum $NO_x$ mixing ratio considered in the experiment is 5 ppt, while the corresponding value in Figure \ref{fig:Sillman1999} is 1 ppb, a negative $O_3$ production rate is seen in our results, whereas it stays out of range of Figure \ref{fig:Sillman1999}.

@@

\section{Results} \label{sec:res}
\subsection{Sensitivity of $O_3$ production to alkyl nitrate chemistry}

A number of simulations for evaluating the sensitivity of the $O_3$ production to alkyl nitrate chemistry were carried out. This was accomplished by switching on and off all reactions present in the chemical mechanism that describe formation or destruction of all alkyl nitrates.

\begin{figure}
\centering
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/noAN/chem_noAN_netO3rate_noINORG_NOx_5ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3rate_noINORG_NOx_5ppt_100ppb.png}
\end{minipage}
\begin{minipage}{.3\textwidth}
  \centering
  \includegraphics[width=.99\linewidth]{D:/FACSIMILE/ANsCBmodel/matlab/ANsCB_pics/ANsNOxVOC/allAN/chem_allAN_netO3ratediff_noINORG_NOx_5ppt_100ppb.png}
\end{minipage}
\caption{Isopleths giving net rate of $O_3$ production (ppb/h, color) as a function of $VOC$ (ppbC) and $NO_x$ (ppb) with alkyl nitrate chemistry switched off (left) and switched on (middle). Difference between them is shown on the right.}
\end{figure}

The simulations that compared ... provided insight into which reactions... under changing $NO_x$ mixing ratios (Table ...).
